## If there is time, we will discuss an interesting example from Setayesh Radkani's research on punishment
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load the data and the libraries

```{r, include=FALSE}
# Load the libraries
library(lme4)
library(multcomp)
#library(lmerTest)
library(ggplot2)
library(dplyr)
library(tidyr)
library(brms)
```

## Load data
```{r, include=FALSE}
### Load the data
# formatted_data.csv is the output of preprocess_data.R script that preprocesses the raw data from Qualtrics.
main_data3 <- read.csv("radkani_punishment_formatted_data_3.csv", header = TRUE) %>% dplyr::select(-c("gender", "age"))    

# combine the Mild and Harsh into a single "Punish" action
punish_data <- main_data3 %>% filter(action %in% c("Mild", "Harsh")) %>% 
  dplyr::select(-c("action", "X", "scenario")) %>%
  dplyr::group_by(participant, LW.condition) %>%
  dplyr::summarise(across(everything(), mean))
punish_data$action <- "Punish"
scenarios <- main_data3 %>% filter(action %in% c("Mild")) %>%
  dplyr::select(c("participant", "LW.condition", "scenario"))
punish_data <- merge(punish_data, scenarios, by=c("participant", "LW.condition"))

none_data <- main_data3 %>% filter(action %in% c("None")) %>%
  dplyr::select(-c("X", "scenario", "action"))
none_data$action <- "None"
none_data <- merge(none_data, scenarios, by=c("participant", "LW.condition"))
main_data5 <- dplyr::bind_rows(punish_data, none_data)
rm(punish_data, none_data)
```

## Understand the structure of the dataset
```{r}
str(main_data5)
```

### A complex model with multiple fixed effects
When participants have a strong prior belief that the target action was not wrong, they do not change this belief much, after observing punishment. We test for an interaction between action (not-punish, punish) and prior condition on the wrongness belief updates, in the “not-wrong” vs “legitimate” conditions. 
```{r}
dat <- main_data5 %>% filter(LW.condition %in% c("Not-wrong", "Legitimate"))
# ideally we want to fit a maximal model for the main effects of legitimacy/wrongness condition + action, but this doesn't work:
m <- lmer(wrongness.change ~ LW.condition * action + (LW.condition * action|participant) + (LW.condition * action|scenario),data=dat,REML=F)
# Let's inspect the structure of the data to better understand the issue
xtabs(~scenario + paste(LW.condition,action), dat) # lots of observations per scenario+condition+action combination. However, we should be cautious about the fact that there are only six scenarios (i.e., few clusters)
xtabs(~participant + paste(LW.condition,action), dat) # but, there are no repeated measures within scenario+condition+action combination! This means that in the above mixed model specification, which has both random participant effects and random trial-level noise, the model is *unidentifiable*: participant-level random effects and trial-level noise cannot be fully distinguished. The key issue is that the sum of independent multivariate normally distributed random variables is also independent multivariate normal.
#myprior <- set_prior("normal(0, 0.01)", class = "sigma")
system.time(m.brm <- brm(wrongness.change ~ LW.condition * action + (LW.condition * action|scenario) + (LW.condition * action|participant),data=dat, save_model="/tmp/radkani-model-code.stan",iter=2,chains=1,warmup=1))
```



```{r}
## For discussing flexible hypothesis testing with a fitted brms model, we will use an under-review dataset from a paper of mine.
#  Download the file here: https://osf.io/n54qb?view_only=c49c658e64eb4f9a8d1d153f3c692898
#  and then read it.
haddock_data <- read_csv("aparicio-etal-exp2.csv")
system.time(exp2.2x3 <- glmer(target ~ adjtype2*displaytype1 +
                              (1+adjtype2*displaytype1 | usernum_unique)+
                              (1+adjtype2*displaytype1 | stimnum),
                            data=haddock_data,
                            family="binomial"))
saveRDS(exp2.2x3,"exp2.2x3.rds")
summary(exp2.2x3)

set.seed(1)
system.time(system.time(exp2.2x3.brm <- brm(target ~ adjtype2*displaytype1 +
                              (1+adjtype2*displaytype1 | usernum_unique)+
                              (1+adjtype2*displaytype1 | stimnum),
                            data=haddock_data,
                            family="bernoulli",
                            control=list(adapt_delta=0.9),
                            iter = 6000)))
saveRDS(exp2.2x3.brm,"exp2.2x3.brm.rds")

```